---
title: "Find art according to age"
author: "Xueying Huang"
date: '2019-12-13'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Find art according to age}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Find those artworks in certain age

In this part, you will use __get_art_age()__ , __sort_time_nation()__ and __get_distribution_country()__ to collect data of artworks and make some summary statistics.

### get_art_age()

You can specify the type of artworks, the start and the end of the period. There are three parameters: Begin, End, class. The defaults of them are: painting artworks during 1600 to 1900.
```{r}
library(pickart)
get_art_age(Begin = 1600, End = 1900, class = "Paintings")
```

When you give a very short period, there might not be artworks match your classificion, the function will give you a warning and you need to re-enter the begin date and end date.
```{r}
get_art_age(Begin = 1620, End = 1650, class = "Sculpture")
```

### sort_time_nation

This function will help you sort the dataframe returned by get_art_age() according to the nationality of artists and created age. The default value is artworks_in_age.
```{r}
sort_time_nation()
```

### get_distribution_country

This function ranks the country according to the number of artworks in the period you choose in get_art_age() function.The default value is artworks_in_age.
```{r}
get_distribution_country()
```
