---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```



# pickart

<!-- badges: start -->
<!-- badges: end -->

## Purpose
The goal of pickart is to help users get detailed information of artworks in the Metropolitan Museum. 

## Installation

You can install the released version of pickart from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("pickart")
```

## Example

This several examples which show you how to use the package:

* Example 1: how many and what kinds of departments the Metropolitan Museum has?

```{r example 1}
library(pickart)
## basic example code
get_departments()
```

## Functionality

There are multiple functions existed in pickart package, these are some examples:

* __get_search_results()__ allows users give a certain theme or topic for searching, and will return the details of all artworks match the query.

* __find_represent_dep()__, __find_represent_artists()__, __get_map()__, __get_related_artworks()__ and __download_details()__ can be used for data analysis and crawl for details of artworks after using the get_search_results() function.

* __get_artworks_in_dep()__ allows users to get details of artworks in certain departments they are interested in.

* __get_popular_perc()__ and __get_popular_items()__ should be used after calling __get_artworks_in_dep()__, they can calculate the percentaeg of popular artworks in each department users choose and tell you what are those popular items.

* __get_art_age()__ allows users to search a type of artworks during a period. Users can specify the type of artworks, the start and the end of the period.

* __sort_time_nation()__ and __get_distribution_country()__ should be used after __get_art_age()__, these functions can achieve sorting according to nationality and make summary statistics about the distribution in different countries.


